\begin{thebibliography}{99}
\addcontentsline{toc}{section}{Literaturverzeichnis}

\bibitem[Beck 98]{Beck98}
	K.\ Beck, W.\ Cunningham, R.\ Jeffries:
	Chrysler Goes To ``Extremes'',
	Distributed Systems: Case Study, S. 25-28 October 1998,
	online abrufbar: \url{http://www.xprogramming.com/publications/dc9810cs.pdf}.

\bibitem[Brown 98]{Brown98}
  W.\ H.\ Brown, R.\ C.\ Malveau, H.\ W.\ McCormick III, et al.:
    Anti Patterns Refactoring Software, Architectures, and Projects in Crisis.
    New York: John Wiley \& Sons, Inc., 1998.

\bibitem[Christian 89]{Christian89}
	F.\ Cristian:
	Probabilistic clock synchronization,
	Distributed Computing (Springer) 3 (3), 1998.

\bibitem[Gamma 94]{Gamma94}
  E.\ Gamma, R.\ Helm, R.\ Johnson, J.\ Vlissides:
    Design Patterns: Elements of Reusable Object-Oriented Software,
	MA: Addison-Wesley, 1994.
	
\bibitem[Ottmann 96]{Ottmann96}
  T.\ Ottmann, P.\ Widmayer:
	Algorithmen und Datenstrukturen-3,
	Heidelberg; Berlin; Oxford: Spektrum, Akad. Verlag 1996.

\bibitem[Schmidt 09]{Schmidt09}
  S. \ Schmidt:
	PHP Design Patterns: Entwurfsmuster für die Praxis.,
	Köln: O'Reilly Verlag, 2. Auflage 2009.

%    Web-References
%______________________________________________________________________

\hspace{-\leftmargin}{\Large\bfseries Web-Referenzen} % Wüster Hack %-|

\bibitem[ARGE Pharmazeutika 07]{PHARMIG07}
	Arbeitsgemeinschaft des pharmazeutischen Großhandels Österreichs:
	Codex für den Transport von Arzneimitteln in Österreich
	\url{http://www.argepgh.at/kwpc_Downloads/Pharmarecht%20%D6sterreich/Codex%20Transport%201007.pdf},
	besucht am 15.03.2011.

\bibitem[CouchDB 11]{CouchDB11}
	Apache CouchDB:
	Technical Overview
	\url{http://couchdb.apache.org/docs/overview.html},
	besucht am 22.06.2011.

\bibitem[Fowler 10]{Fowler10}
	M.\ Fowler:
	Richardson Maturity Model: Steps towards the glory of REST
	\url{http://martinfowler.com/articles/richardsonMaturityModel.html},
	besucht am 20.06.2011.
	
\bibitem[Internet Engineering Task Force 11]{IETF11}
	Internet Engineering Task Force:
	A JSON Media Type for Describing the Structure and Meaning of JSON Documents
	\url{http://tools.ietf.org/html/draft-zyp-json-schema-03},
	besucht am 11.05.2011.

\bibitem[Murphy 09]{Murphy09}
	E.\ Murphy:
	CouchDB in Ubuntu
	\url{http://mail-archives.apache.org/mod_mbox/couchdb-dev/200910.mbox/%3C4AD53996.3090104@canonical.com%3E}, besucht am 16.06.2011.

\bibitem[Open Handset Alliance 07]{OHA07}
  Open Handset Alliance
    \url{http://www.openhandsetalliance.com/press_110507.html}, besucht am 23.06.2011.

\bibitem[Torvalds 07]{Torvalds07}
	Linus Torvalds (2005-04-07).
	``Re: Kernel SCM saga..''.
	The linux-kernel mailing list. ``So I'm writing some scripts to try to track
	things a whole lot faster.''
	\url{http://marc.info/?l=linux-kernel&m=111288700902396}, besucht am 18.06.2011.

\bibitem[W3C 11]{W3C11}
	W3C Working Draft 7 April 2011:
	Grid Layout
	\url{http://www.w3.org/TR/css3-grid-layout/}, besucht am 22.06.2011.

\bibitem[Wikipedia 10a]{Wikipedia10a}
  Wikipedia: Node.js
    \url{http://de.wikipedia.org/wiki/Node.js}, besucht am 20.04.2011.
	
\end{thebibliography}